Supplementary Material for: A Rough Guide to Pre-processing High-Frequency Animal Tracking Data

### 2020-11-23 docs/supplementary_material.tex
add sup mat text

\documentclass[]{scrartcl}

@@

\newcommand{\AlertTok}[1]{\textcolor[rgb]{1.00,0.00,0.00}{\textbf{#1}}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{#1}}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.49,0.56,0.16}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{#1}}

@@

\newcommand{\CharTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textit{#1}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{#1}}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.53,0.00,0.00}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.00,0.44,0.13}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.56,0.13,0.00}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.73,0.13,0.13}{\textit{#1}}}

@@

\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.02,0.16,0.49}{#1}}

@@

\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{#1}}}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.00,0.44,0.13}{\textbf{#1}}}

@@

\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.40,0.40,0.40}{#1}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.00,0.44,0.13}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.74,0.48,0.00}{#1}}

@@

\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.73,0.40,0.53}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.10,0.09,0.49}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{#1}}}}

@@

\usepackage{lineno}

@@

{
\setcounter{tocdepth}{2}
\tableofcontents
}
\hypertarget{processing-calibration-data}{%
\section{Processing calibration data}\label{processing-calibration-data}}

@@

\hypertarget{prepare-libraries}{%
\subsection{Prepare libraries}\label{prepare-libraries}}

@@

\hypertarget{access-data-and-preliminary-visualisation}{%
\subsection{Access data and preliminary visualisation}\label{access-data-and-preliminary-visualisation}}

@@

\hypertarget{filter-by-bounding-box}{%
\subsection{Filter by bounding box}\label{filter-by-bounding-box}}

@@

\hypertarget{filter-trajectories}{%
\subsection{Filter trajectories}\label{filter-trajectories}}

\hypertarget{handle-time}{%
\subsubsection{Handle time}\label{handle-time}}

@@

\hypertarget{add-speed-and-turning-angle}{%
\subsubsection{Add speed and turning angle}\label{add-speed-and-turning-angle}}

@@

\hypertarget{get-95th-percentile-of-speed-and-angle}{%
\subsubsection{Get 95th percentile of speed and angle}\label{get-95th-percentile-of-speed-and-angle}}

@@

\hypertarget{filter-on-speed}{%
\subsubsection{Filter on speed}\label{filter-on-speed}}

@@

\hypertarget{smoothing-the-trajectory}{%
\subsection{Smoothing the trajectory}\label{smoothing-the-trajectory}}

@@

\hypertarget{thinning-the-data}{%
\subsection{Thinning the data}\label{thinning-the-data}}

@@

\hypertarget{residence-patches}{%
\subsection{Residence patches}\label{residence-patches}}

\hypertarget{get-waypoint-centroids}{%
\subsubsection{Get waypoint centroids}\label{get-waypoint-centroids}}

@@

\hypertarget{prepare-data}{%
\subsubsection{Prepare data}\label{prepare-data}}

@@

\hypertarget{calculate-residence-time}{%
\subsubsection{Calculate residence time}\label{calculate-residence-time}}

@@

\hypertarget{run-residence-patch-method}{%
\subsubsection{Run residence patch method}\label{run-residence-patch-method}}

@@

\hypertarget{get-spatial-and-summary-objects}{%
\subsubsection{Get spatial and summary objects}\label{get-spatial-and-summary-objects}}

@@

\hypertarget{prepare-to-plot-data}{%
\subsubsection{Prepare to plot data}\label{prepare-to-plot-data}}

@@

\hypertarget{compare-patch-metrics}{%
\subsection{Compare patch metrics}\label{compare-patch-metrics}}

@@

\hypertarget{linear-model-durations}{%
\subsubsection{Linear model durations}\label{linear-model-durations}}

@@

\hypertarget{linear-model-summary}{%
\subsubsection{Linear model summary}\label{linear-model-summary}}

@@

\hypertarget{processing-egyptian-fruit-bat-tracks}{%
\section{Processing Egyptian fruit bat tracks}\label{processing-egyptian-fruit-bat-tracks}}

@@

\hypertarget{prepare-libraries-1}{%
\subsection{Prepare libraries}\label{prepare-libraries-1}}

@@

\hypertarget{install-atlastools-from-github.}{%
\subsection{\texorpdfstring{Install \texttt{atlastools} from Github.}{Install atlastools from Github.}}\label{install-atlastools-from-github.}}

@@

\hypertarget{read-bat-data}{%
\subsection{Read bat data}\label{read-bat-data}}

@@

\hypertarget{a-first-visual-inspection}{%
\subsection{A First Visual Inspection}\label{a-first-visual-inspection}}

@@

\hypertarget{prepare-data-for-filtering}{%
\subsection{Prepare data for filtering}\label{prepare-data-for-filtering}}

@@

\hypertarget{prepare-data-per-individual}{%
\subsubsection{Prepare data per individual}\label{prepare-data-per-individual}}

@@

\hypertarget{filter-by-covariates}{%
\subsection{Filter by covariates}\label{filter-by-covariates}}

@@

\hypertarget{sanity-check-plot-filtered-data}{%
\subsubsection{Sanity check: Plot filtered data}\label{sanity-check-plot-filtered-data}}

We plot the data to check whether the filtering has improved the data (Figure 2).
The plot code is once again hidden in this rendering, but is available in the source code file.

@@

\hypertarget{filter-by-speed}{%
\subsection{Filter by speed}\label{filter-by-speed}}

@@

\hypertarget{sanity-check-plot-speed-filtered-data}{%
\subsubsection{Sanity check: Plot speed filtered data}\label{sanity-check-plot-speed-filtered-data}}

The speed filtered data is now inspected for errors (Figure 3). The plot code is once again hidden.

@@

\hypertarget{median-smoothing}{%
\subsection{Median smoothing}\label{median-smoothing}}

The quality of this data (Figure 3) is relatively high, and a median smooth is not strictly necessary. We demonstrate the application of a 5 point median smooth to the data nonetheless.

@@

\hypertarget{sanity-check-plot-smoothed-data}{%
\subsubsection{Sanity check: Plot smoothed data}\label{sanity-check-plot-smoothed-data}}

@@

\hypertarget{making-residence-patches}{%
\subsection{Making residence patches}\label{making-residence-patches}}

\hypertarget{calculating-residence-time}{%
\subsubsection{Calculating residence time}\label{calculating-residence-time}}

@@

\hypertarget{constructing-residence-patches}{%
\subsubsection{Constructing residence patches}\label{constructing-residence-patches}}

@@

\hypertarget{getting-residence-patch-data}{%
\subsubsection{Getting residence patch data}\label{getting-residence-patch-data}}

We extract the residence patch data as spatial \texttt{sf-MULTIPOLYGON} objects.
These are returned as a list and must be converted into a single \texttt{sf} object.
These objects and the raw movement data are shown in Figure 5.

@@

\hypertarget{write-patch-spatial-representations}{%
\subsubsection{Write patch spatial representations}\label{write-patch-spatial-representations}}

@@

\hypertarget{references}{%
\section{References}\label{references}}

>>>>

\documentclass[]{scrreprt}

@@

\newcommand{\AlertTok}[1]{\textcolor[rgb]{1.00,0.00,0.00}{#1}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.00,0.50,0.00}{#1}}
\newcommand{\AttributeTok}[1]{#1}
\newcommand{\BaseNTok}[1]{#1}

@@

\newcommand{\CharTok}[1]{\textcolor[rgb]{0.00,0.50,0.50}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.00,0.50,0.00}{#1}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.00,0.50,0.00}{#1}}
\newcommand{\ConstantTok}[1]{#1}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.00,0.00,1.00}{#1}}
\newcommand{\DataTypeTok}[1]{#1}
\newcommand{\DecValTok}[1]{#1}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.00,0.50,0.00}{#1}}

@@

\newcommand{\FloatTok}[1]{#1}
\newcommand{\FunctionTok}[1]{#1}

@@

\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.00,0.50,0.00}{#1}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.00,0.00,1.00}{#1}}

@@

\newcommand{\OperatorTok}[1]{#1}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{1.00,0.25,0.00}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{1.00,0.25,0.00}{#1}}

@@

\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.50,0.50}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.00,0.50,0.50}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.00,0.50,0.50}{#1}}
\newcommand{\VariableTok}[1]{#1}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.00,0.50,0.50}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.00,0.50,0.00}{\textbf{#1}}}

@@

\usepackage{lineno}
\KOMAoption{fontsize}{10pt}

@@

{
\setcounter{tocdepth}{1}
\tableofcontents
}
\hypertarget{processing-calibration-data}{%
\chapter{Processing calibration data}\label{processing-calibration-data}}

@@

\hypertarget{prepare-libraries}{%
\section{Prepare libraries}\label{prepare-libraries}}

@@

\hypertarget{access-data-and-preliminary-visualisation}{%
\section{Access data and preliminary visualisation}\label{access-data-and-preliminary-visualisation}}

@@

\hypertarget{filter-by-bounding-box}{%
\section{Filter by bounding box}\label{filter-by-bounding-box}}

@@

\hypertarget{filter-trajectories}{%
\section{Filter trajectories}\label{filter-trajectories}}

\hypertarget{handle-time}{%
\subsection{Handle time}\label{handle-time}}

@@

\hypertarget{add-speed-and-turning-angle}{%
\subsection{Add speed and turning angle}\label{add-speed-and-turning-angle}}

@@

\hypertarget{get-95th-percentile-of-speed-and-angle}{%
\subsection{Get 95th percentile of speed and angle}\label{get-95th-percentile-of-speed-and-angle}}

@@

\hypertarget{filter-on-speed}{%
\subsection{Filter on speed}\label{filter-on-speed}}

@@

\hypertarget{smoothing-the-trajectory}{%
\section{Smoothing the trajectory}\label{smoothing-the-trajectory}}

@@

\hypertarget{thinning-the-data}{%
\section{Thinning the data}\label{thinning-the-data}}

@@

\hypertarget{residence-patches}{%
\section{Residence patches}\label{residence-patches}}

\hypertarget{get-waypoint-centroids}{%
\subsection{Get waypoint centroids}\label{get-waypoint-centroids}}

@@

\hypertarget{prepare-data}{%
\subsection{Prepare data}\label{prepare-data}}

@@

\hypertarget{calculate-residence-time}{%
\subsection{Calculate residence time}\label{calculate-residence-time}}

@@

\hypertarget{run-residence-patch-method}{%
\subsection{Run residence patch method}\label{run-residence-patch-method}}

@@

\hypertarget{get-spatial-and-summary-objects}{%
\subsection{Get spatial and summary objects}\label{get-spatial-and-summary-objects}}

@@

\hypertarget{prepare-to-plot-data}{%
\subsection{Prepare to plot data}\label{prepare-to-plot-data}}

@@

\hypertarget{compare-patch-metrics}{%
\section{Compare patch metrics}\label{compare-patch-metrics}}

@@

\hypertarget{linear-model-durations}{%
\subsection{Linear model durations}\label{linear-model-durations}}

@@

\hypertarget{linear-model-summary}{%
\subsection{Linear model summary}\label{linear-model-summary}}

@@

\hypertarget{processing-egyptian-fruit-bat-tracks}{%
\chapter{Processing Egyptian fruit bat tracks}\label{processing-egyptian-fruit-bat-tracks}}

@@

\hypertarget{prepare-libraries-1}{%
\section{Prepare libraries}\label{prepare-libraries-1}}

@@

\hypertarget{install-atlastools-from-github.}{%
\section{\texorpdfstring{Install \texttt{atlastools} from Github.}{Install atlastools from Github.}}\label{install-atlastools-from-github.}}

@@

\hypertarget{read-bat-data}{%
\section{Read bat data}\label{read-bat-data}}

@@

\hypertarget{a-first-visual-inspection}{%
\section{A First Visual Inspection}\label{a-first-visual-inspection}}

@@

\hypertarget{prepare-data-for-filtering}{%
\section{Prepare data for filtering}\label{prepare-data-for-filtering}}

@@

\hypertarget{prepare-data-per-individual}{%
\subsection{Prepare data per individual}\label{prepare-data-per-individual}}

@@

\hypertarget{filter-by-covariates}{%
\section{Filter by covariates}\label{filter-by-covariates}}

@@

\hypertarget{sanity-check-plot-filtered-data}{%
\subsection{Sanity check: Plot filtered data}\label{sanity-check-plot-filtered-data}}

We plot the data to check whether the filtering has improved the data (Figure 9).
The plot code is once again hidden in this rendering, but is available in the source code file.

@@

\hypertarget{filter-by-speed}{%
\section{Filter by speed}\label{filter-by-speed}}

@@

\hypertarget{sanity-check-plot-speed-filtered-data}{%
\subsection{Sanity check: Plot speed filtered data}\label{sanity-check-plot-speed-filtered-data}}

The speed filtered data is now inspected for errors (Figure 10). The plot code is once again hidden.

@@

\hypertarget{median-smoothing}{%
\section{Median smoothing}\label{median-smoothing}}

The quality of this data (Figure 10) is relatively high, and a median smooth is not strictly necessary. We demonstrate the application of a 5 point median smooth to the data nonetheless.

@@

\hypertarget{sanity-check-plot-smoothed-data}{%
\subsection{Sanity check: Plot smoothed data}\label{sanity-check-plot-smoothed-data}}

@@

\hypertarget{making-residence-patches}{%
\section{Making residence patches}\label{making-residence-patches}}

\hypertarget{calculating-residence-time}{%
\subsection{Calculating residence time}\label{calculating-residence-time}}

@@

\hypertarget{constructing-residence-patches}{%
\subsection{Constructing residence patches}\label{constructing-residence-patches}}

@@

\hypertarget{getting-residence-patch-data}{%
\subsection{Getting residence patch data}\label{getting-residence-patch-data}}

We extract the residence patch data as spatial \texttt{sf-MULTIPOLYGON} objects.
These are returned as a list and must be converted into a single \texttt{sf} object.
These objects and the raw movement data are shown in Figure 12.

@@

\hypertarget{write-patch-spatial-representations}{%
\subsection{Write patch spatial representations}\label{write-patch-spatial-representations}}

@@

\hypertarget{references}{%
\chapter{References}\label{references}}
